Personal Research and Articles

### 2024-05-09 articles.qmd
Update

---
title: "Singapore's Public Housing Affordability"
---

@@

## Is Public Housing Affordable for Singaporeans?

@@

In Singapore, housing affordability has been an increasing worry for future Singaporeans. However, in 2012, the then Deputy Prime Minister (DPM) Tharman Shanmugaratnam - stating household income of SGD\$1000 was sufficient to own a home, sparked discussions among netizen online (Tan, 2012).

@@

>>>>

---
title: "Personal Research and Articles"
---

![](docs/src/images/research.jpeg)

Here, I have undertaken multiple personal research projects based on my interests. While these initiatives are just for my own skill enhancement, they reflect my commitment to continuously improving my data analysis capabilities. Through these projects, I delve into various datasets, exploring patterns and extracting actionable insights. <br> <br> This portfolio showcases my journey, illustrating not only my technical skills but also my curiosity and dedication to leveraging data in meaningful ways. Each project here is a step towards mastering the art of transforming raw data into compelling narratives and informed decisions. Happy reading!

<details>

<summary> Singapore's Public Housing Affordability <br> <p style="text-align: justify;">

In Singapore, housing affordability has been an increasing worry for future Singaporeans. However, in 2012, the then Deputy Prime Minister (DPM) Tharman Shanmugaratnam - stating household income of SGD\$1000 was sufficient to own a home, sparked discussions among netizen online (Tan, 2012). Read more here...

</summary>

## Is Public Housing Affordable for Singaporeans?
<p style="text-align: right;">  Monday, 6 Nov 2023 </p>

@@

@@

@@

</details>

<details>

<summary> Educational Deviance in Singapore: A Case Study of Truancy and Societal Reaction <br> <p style="text-align: justify;">

This study examines the impact of labeling on student identity within Singapore's educational system through the case of "Jeremy," a student labeled as a "truant." Utilizing a life history interview, the research illustrates how societal reactions and the Compulsory Education Act of 2000 influence behaviors from primary to secondary deviance. Read more here...

</summary>

## Who Determines Deviant Behaviour?

<p style="text-align: right;">  Friday, 10 May 2024 </p>

![](docs/src/images/school.avif)

<p style="text-align: right;">
    Photo Source: CNA
</p>
The findings emphasize the detrimental effects of punitive measures and highlight the need for supportive reintegration strategies. This case underscores the broader implications for educational policy and practices in managing deviance constructively.

### Background
![](docs/src/images/soon.avif){width="730"}

</details>
